outline!

### 2016-05-17 paper.tex
paper: updates
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

There is a finite set of strategies for mapping the CORFU interfaces onto the
current set of native I/O interfaces used to construct object interfaces.
Table~\ref{tab:pd-map} shows the design space for mapping the CORFU interfaces
onto Ceph. In order to select the best mapping we performed a parameter sweet
over the design space.

\begin{figure*}[!ht]
    \centering
    \begin{subfigure}{.6\columnwidth}
        \includegraphics[width=\columnwidth]{experiments/librados-sweep/jewel_ssd.png}
        \caption{a}
        \label{fig:vanilla-io-diff}
    \end{subfigure}\hfill
    \begin{subfigure}{.6\columnwidth}
        \includegraphics[width=\columnwidth]{experiments/librados-sweep/firefly_ssd.png}
        \caption{b}
    \end{subfigure}\hfill
    \begin{subfigure}{.6\columnwidth}
        \includegraphics[width=\columnwidth]{experiments/basic-cls-overhead/output.1024.soft.reset.png}
        \caption{c}
    \end{subfigure}\hfill
    \caption{Shown here are the graphs and such that demonstrate that the same
        physical design choices are not the same between differing version of
    Ceph even on the same hardware.}
\end{figure*}

Figure~\ref{fig:vanilla-io-diff} shows the result of a parameter sweep which
clearly shows that an N-1 mapping based on the bytestream interface provides
superiour performance. However, the other two graphs show the same interfaces
running on an old version of Ceph that show the same decision would not have
been the optimal choice {\bf \emph{note: for the outline these are not the
real graphs we'll be using}}.

\begin{table}
\begin{tabular}{ | l | l | l | l | l |}
\hline
Map & I/O & Entry Size & Addressing & Metadata \\ \hline
\multirow{3}{*}{1:1} & KV  & Flex     & Ceph      & KV/BS \\ \cline{2-5}
                     & BS  & Flex     & Ceph/VFS  & KV/BS \\ \hline
\multirow{4}{*}{N:1} & KV  & Flex     & \multicolumn{2}{|c|}{KV/BS} \\ \cline{2-5}
                     & WR  & Fixed    & VFS       & KV/BS \\ \cline{2-5}
                     & AP  & Flex     & KV/BS     & KV/BS \\
\hline
\end{tabular}
\caption{The high-level design space of mapping CORFU log entry storage onto
the RADOS object storage system.}
\label{tab:pd-map}
\end{table}

>>>>

As we have seen, Ceph provides a rich storage API and places few restrictions
on the structure of applications. So how should we go about implementing CORFU
on Ceph? Our strategy is straightforward: first we will define the entire
design space, and we will then winnow down this space using a set of targetted
benchmarks. The design space can be divided into three challenges:
selecting a strategy for log entry addressing, choosing a native I/O interface
for storing log entry content, and implementing efficient metadata management.

\begin{enumerate}
    \item {\bf Entry addressing.} We refer to the method by which a client
        locates a log entry in Ceph as entry addressing, and we consider two
        strategies. In a one-to-one (1:1) strategy each log entry is stored in
        a distinct object with a name derived from the associated log entry
        position. This is an attractive option because it is trivial for
        clients to locate a log entry given its position.  In contrast, an N:1
        strategy \emph{stripes} log entires across a smaller set of objects,
        but adds complexity to both the client and the object interface which
        must multiplex a set of entries.

    \item {\bf Log entry storage.} Clients read and write binary data
        associated with each log entry, and these entries can be stored in the
        bytestream or in the key-value database associated with an object.
        Retrieval of log entry payloads should perform well for both large
        (e.g. database checkpoint) and small log entries.

    \item {\bf Metadata management.} The CORFU protocol defines the storage
        interface semantics, such as enforcing up-to-date epoch values and a
        write-once address space. The object interface constructed in Ceph must
        implement these semantics in software by storing metadata (e.g. the
        current epoch) and validating requests against this metadata (e.g. has
        the target position been written?). A key-value store is a natural
        location for this type of data, but metadata management adds overhead
        to each request and must be carefully designed.
\end{enumerate}

In the remainder of this section we will explore the full design space defined
by the cross product of these design challenges to arrive at a final design.
In order to optimize this process we will iteratively winnow down the space
through a series of targetted experiments.

\paragraph*{Baseline Entry Storage Performance}
We begin the process of exploring the design space by exploiting the fact that
metadata management is a complexity and performance overhead that a full
implementation must incur beyond the costs of storing log entry data.
Therefore we first explore the costs of the design space by restricting the
space to log entry addressing and log entry storage.  These two dimensions are
represented by the first two columns of Table~\ref{tab:pd-map} which describes
the entire design space. In the I/O column \emph{KV} corresponds to the
key-value interface, and the bytestream interface is represented by \emph{AP}
for an append strategy, and \emph{EX} for a strategy that writes to an
explicit bytestream offset.

%\begin{figure}
%\centering
%\includegraphics[width=\columnwidth]{experiments/librados-sweep/jewel_ssd.png}
%\caption{1hr, 1k, write}
%\label{fig:vanilla_wr_jewel}
%\end{figure}

Figure~\ref{fig:vanilla_wr_jewel} shows the expected performance of 1K log
appends without metadata management overhead using each of the five strategies
defined in Table~\ref{tab:pd-map}. The first thing to notice in this figure is
that both one-to-one strategies have relatively poor performance. The large
period of reduced throughput for \emph{11wr} corresponds to the OSD splitting
file system directories in order to maintain a maximum directory size, and
will occur in \emph{11kv} although the threshold number of objects is not
reached due to reduced overall throughput of the \emph{11kv} strategy.

The second lesson that we can learn from Figure~\ref{fig:vanilla_wr_jewel} is
that even when using an N:1 addressing strategy, the key-value interface
imposes a large overhead. This is unfortuante because the key-value interface
can provide a direct solution to addressing log entries within an object.
Instead, what we find is that an N:1 addressing strategy that stores log
entries in the bytestream using either object appends or writes to explicit
offsets outperform all other strategies by a factor of over 2x.

The apparent performance tie between the strategies of appending to an object
and writing to explicit offsets can be broken by considering the flexibility
offered by each approach. The third column \emph{entry size} shown in
Table~\ref{tab:pd-map} lists if a particular strategy supports storage of
entries with dynamic sizes, or if entries must be restricted to a fixed size.
Notably the strategy that stores log entries at explicit object offsets is
limited in this regard because each log entry is effectively pre-mapped into
the storage system. This leaves the clear winner: an N:1 strategy that appends
log entries to objects provides flexibilty and the best write performance in
this particular configuration.

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{.47\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{experiments/librados-sweep/jewel_ssd.png}
      \caption{1hr,1k,wr}
      \label{fig:osdx}
  \end{subfigure}\quad
  \begin{subfigure}[b]{.47\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{experiments/basic-cls-rand-read/output.read.60min.1k.png}
      \caption{1hr,1k,rd}
      \label{fig:cephx}
  \end{subfigure}
  \caption{Ceph and OSD... gotta cram more stuff in here...}
\end{figure}

%\begin{figure}
%\centering
%\includegraphics[width=\columnwidth]{experiments/basic-cls-rand-read/output.read.60min.1k.png}
%\caption{1hr, 1k, read}
%\label{fig:vanilla_rd_jewel}
%\end{figure}

This result is corroborated by considering the read performance for each
strategy as well. Figure~\ref{fig:vanilla_rd_jewel} shows the expected random
read performance from a log containing 1K entries in which an addressing
strategy that stores log entries in the bytestream has the best performance.

\begin{table}
\begin{tabular}{ | l | l | l | l | l |}
\hline
Map & I/O & Entry Size & Addressing & Metadata \\ \hline
\multirow{3}{*}{1:1} & KV  & Flex     & Ceph      & KV/BS \\ \cline{2-5}
                     & AP  & Flex     & Ceph/VFS  & KV/BS \\ \hline
\multirow{4}{*}{N:1} & KV  & Flex     & \multicolumn{2}{|c|}{KV/BS} \\ \cline{2-5}
                     & EX  & Fixed    & VFS       & KV/BS \\ \cline{2-5}
                     & AP  & Flex     & KV/BS     & KV/BS \\
\hline
\end{tabular}
\caption{The high-level design space of mapping CORFU log entry storage onto
the RADOS object storage system.}
\label{tab:pd-map}
\end{table}
